---
title: "Metrics and Labels"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{metrics-and-labels}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 5
)
```

```{r setup, include = FALSE}
library(ggwaterfall)
```

Metrics and labels are powerful arguments which can add more useful data on a
waterfall plot.
Below you can find a few examples.

## Show labels

If `show.label` is `TRUE`, you will see labels on the right side of your plots.
By default, the label for each plot is its indexes in the original list:

```{r indxes}
data <- list(
  rnorm(100, 0),
  rnorm(100, 40),
  rnorm(100, 20)
)
waterfall_density(data, show.labels = TRUE)
```

If you are using named elements in your list, the names will be displayed
instead of indexes:

```{r names}
data <- list(
  a = rnorm(100, 0),
  b = rnorm(100, 40),
  c = rnorm(100, 20)
)
waterfall_density(data, show.labels = TRUE)
```

## Show metrics

If `metric` is defined, it will be displayed instead of indexes:

```{r metrics}
data <- list(
  rnorm(100, 0),
  rnorm(100, 40),
  rnorm(100, 20)
)
waterfall_density(data, metric = "mean", show.labels = TRUE)
```

## Sort by metric

With the help of `sort.order` argument, you can sort all of your plots by the
metric value:

```{r sort}
waterfall_density(rdistrs(20), metric = "mean", sort.value = "metric",
                  show.labels = TRUE)
```

## Custom label function

You can provide own function which can be used for label generation:

```{r custom-label}
custom_label <- function(index, name, metric.value) {
  paste0(index, ":", round(metric.value))
}
waterfall_density(rdistrs(5), metric = mean, calc.label = custom_label,
                  show.labels = TRUE)
```

## Custom label width

If you have long labels, the space for labels can be increased via
`label.expand`:

```{r custom-width}
custom_label <- function(index, name, metric.value) {
  paste(replicate(index, letters[index]), collapse = "")
}
waterfall_density(rdistrs(7), metric = mean, calc.label = custom_label,
                  show.labels = TRUE, label.expand = 0.2)
```