---
title: "Palettes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{palettes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 5
)
```

```{r setup, include = FALSE}
library(ggwaterfall)
```

With the help of the `palette` argument (the second argument of
`waterfall_density` and `waterfall_ft`) allows you to customize the fill colors
of your plot.

Below you can find several nice looking color palettes.

## Rainbow

```{r rainbow}
waterfall_density(rdistrs(20), rainbow(7))
```

## Heatmap

```{r heatmap}
waterfall_density(rdistrs(20), colorRampPalette(c("red", "orange"))(8))
```

## Yellow

```{r yellow}
waterfall_density(rdistrs(20), colorRampPalette(c("yellow", "yellow4"))(9))
```

## Blue

```{r blue}
waterfall_density(rdistrs(20), colorRampPalette(c("royalblue", "royalblue4"))(10))
```

## Purple

```{r purple}
waterfall_density(rdistrs(20), colorRampPalette(c("purple", "purple4"))(11))
```

## Green

```{r green}
waterfall_density(rdistrs(20), colorRampPalette(c("green2", "green4"))(12))
```

## Pulsar style

With the help of `style.pulsar`, you can apply the plot style which is similar
to the iconic plot of a pulsar and the
["Unknown Pleasures"](https://en.wikipedia.org/wiki/Unknown_Pleasures) Joy
Division album cover. If it's true, the values of `palette`, `bg`, `col`,
`alpha`, `show.axis`, `show.underline` will be ignored because they will be
overriden by special values which are specific for the pulsar style images.

```{r pulsar}
waterfall_density(rdistrs(20), style.pulsar = TRUE)
```